### 2018-05-15 submission/manuscript.tex
complete removal of sub-sampling

\textbf{\emph{Analysis Workflow:}} All samples were rarefied to 1000
sequence. The total number of OTUs was analyzed for both the fecal and
mock community samples. For fecal samples, cycle dependent affects on
Bray-Curtis indices were assessed for cycle group and within individual
differences from the previous cycle (e.g.~20 versus 25, 25 versus 30,
etc.). Based on these observations we analyzed potential reasons for
these differences. Analysis of the mock community of each HiFi DNA
polymerase for general sequence error rate, number of sequences with an
error, base substitution, and numbers of chimeras were assessed before
and after chimera removal. Additionally, the correlation between the
number of chimeras and the number of OTUs was also assessed.

@@

There were few differences that depend on HiFi DNA polymerase for
between sample diversity, as measured by the Bray-Curtis index. Using
this metric our observations found no differences in the overall
bacterial community composition for sub-sampling depth or cycle number
used. One possible reason for this outcome was that our study did not
have enough power to detect differences due to low sample number in each
group. Another reason was that many of the OTUs are likely not highly
abundant, allowing the Bray-Curtis index to be able to successfully
down-weight chimeric OTUs (Minchin, 1987). The choice of downstream
diversity metric could be an important consideration in helping to
mitigate these observed HiFi DNA polymerase dependent differences in
chimera prevalence. Metrics that solely use presence/absence of OTUs
(e.g.~Jaccard (Real \& Vargas, 1996)) may be less robust to chimera
prevalence and by extension total number of OTU differences in HiFi DNA
Polymerases. When choosing a distance metric, careful consideration of
the biases introduced from the PCR step of the 16S rRNA gene sequencing
workflow need to be taken into account. With differences in the number
of OTUs and chimera prevalence depending on HiFi DNA polymerase used, it
might be easier to avoid specific DNA polymerase families altogether.

>>>>

\textbf{\emph{Analysis Workflow:}} All samples were rarefied to 1000
sequence. The total number of OTUs was analyzed for both the fecal and
mock community samples. For fecal samples, cycle dependent affects on
Bray-Curtis indices were assessed for cycle group and within individual
differences from the previous cycle (e.g.~20 versus 25, 25 versus 30).
Based on these observations we analyzed potential reasons for these
differences. Analysis of the mock community of each HiFi DNA polymerase
for general sequence error rate, number of sequences with an error, base
substitution, and numbers of chimeras were assessed before and after
chimera removal. Additionally, the correlation between the number of
chimeras and the number of OTUs was also assessed.

@@

There were few differences that depend on HiFi DNA polymerase for
between sample diversity, as measured by the Bray-Curtis index. Using
this metric our observations generally found no differences in the
overall bacterial community composition for the number of cycles used.
One possible reason for this outcome was that our study did not have
enough power to detect differences due to low sample number in each
group. Another reason was that many of the OTUs are likely not highly
abundant, allowing the Bray-Curtis index to be able to successfully
down-weight chimeric OTUs (Minchin, 1987). The choice of downstream
diversity metric could be an important consideration in helping to
mitigate these observed HiFi DNA polymerase dependent differences in
chimera prevalence. Metrics that solely use presence/absence of OTUs
(e.g.~Jaccard (Real \& Vargas, 1996)) may be less robust to chimera
prevalence and by extension total number of OTU differences in HiFi DNA
Polymerases. When choosing a distance metric, careful consideration of
the biases introduced from the PCR step of the 16S rRNA gene sequencing
workflow need to be taken into account. With differences in the number
of OTUs and chimera prevalence depending on HiFi DNA polymerase used, it
might be easier to avoid specific DNA polymerase families altogether.
